A new machine-learning-based prediction of survival in patients with end-stage liver disease

### 2022-11-27 analysis/supplement.Rmd
refactor: change supplemental figure 2.1 according to reviewer's suggestions

```{r benchmark-plot, fig.cap = "Benchmark results of machine-learning algorithms.", echo = FALSE, fig.width = 18, fig.height = 12}
tar_load(bmrk_results)
r <- bmrk_results$clone()
id <- grep("^scale", x = r$learners$learner_id, invert = TRUE, value = TRUE)
r$filter(task_id = "zlog_eldd", learner_id = id)
autoplot(r) +
    geom_boxplot(aes(fill = learner_id)) +
    geom_jitter(position = position_jitter(0.2)) +
    scale_fill_viridis(discrete = TRUE) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

```{r benchmark-table, echo = FALSE}
agg <- bmrk_results$aggregate(msr("surv.cindex", id = "harrell"))
agg[, `:=`
    (nr = NULL, resample_result = NULL, resampling_id = NULL, iters = NULL)
]
agg <- subset(agg, task_id == "zlog_eldd" & !grepl("^scale", learner_id))
agg[, task_id := NULL]
setorder(agg, -harrell)
knitr::kable(
    agg,
    col.names = c("Learner ID", "Harrell C"),
    caption = paste0("Benchmark results. Ranking of the ", nrow(agg), " tested machine-learning algorithms.")
)
```

>>>>

```{r benchmark-plot, fig.cap = "Benchmark results of machine-learning algorithms.", echo = FALSE, fig.width = 18, fig.height = 12}
tar_load(bmrk_results)
r <- bmrk_results$clone()
id <- grep("^scale", x = r$learners$learner_id, invert = TRUE, value = TRUE)
r$filter(task_id = "zlog_eldd", learner_id = id)

relabel_learners <- function(x) {
    x <- gsub("\\.tuned", "", x)
    x <- gsub("1$", "", x)
    x <- gsub("^surv\\.", "", x)
    x
}

## taken from mlr3viz::autoplot.BenchmarkResults
task <- r$tasks$task[[1L]]
measure <- mlr3::assert_measure(mlr3::as_measure(msr("surv.cindex"), task_type = task$task_type), task = task)
measure_id <- measure$id
tab <- fortify(r, measure = measure)
tab$nr <- sprintf("%09d", tab$nr)
tab$learner_id <- relabel_learners(tab$learner_id)
tab$group <- tab$learner_id
tab$group[tab$group == "xgboost"] <- "boosting"
tab$group[grepl("lasso|ridge|net", tab$group)] <- "penalized regression"
tab$group[grepl("svm", tab$group)] <- "svm"
tab$group[tab$group %in% c("ranger", "rfsrc")] <- "random forests"
tab$group[tab$group %in% c("coxtime", "deepsurv")] <- "neural networks"
tab$group <- factor(
    tab$group,
    levels = c(
        "cox", "penalized regression",
        "random forests", "boosting", "svm", "neural networks"
    )
)
learner_label_map <- tab[!duplicated(tab$nr), c("nr", "learner_id")]
learner_labels <- learner_label_map$learner_id
names(learner_labels) <- learner_label_map$nr
ggplot(tab, mapping = aes(x = .data$nr, y = .data[[measure_id]])) +
    geom_boxplot(aes(fill = .data$group)) +
    labs(fill = "Algorithm category") +
    labs(y = "Harrell's concordance index") +
    labs(x = "Model") +
    scale_x_discrete(labels = learner_labels) +
    scale_fill_viridis(labels = learner_labels, discrete = TRUE, option = "cividis") +
    facet_grid(cols = vars(group), scales = "free_x", space = "free") +
    mlr3viz:::apply_theme(list(theme_mlr3())) +
    geom_jitter(position = position_jitter(0.2)) +
    theme(
        legend.position = "none",
        strip.text.x = element_text(size = 20),
        text = element_text(size = 24),
        axis.text.x = element_text(angle = 45, hjust = 1)
    )
```

```{r benchmark-table, echo = FALSE}
agg <- bmrk_results$aggregate(msr("surv.cindex", id = "harrell"))
agg[, `:=`
    (nr = NULL, resample_result = NULL, resampling_id = NULL, iters = NULL)
]
agg <- subset(agg, task_id == "zlog_eldd" & !grepl("^scale", learner_id))
agg[, task_id := NULL]
setorder(agg, -harrell)
agg$name <- relabel_learners(agg$learner_id)
knitr::kable(
    agg[, list(name, learner_id, harrell)],
    col.names = c("Model", "Learner ID", "Harrell C"),
    caption = paste0("Benchmark results. Ranking of the ", nrow(agg), " tested machine-learning algorithms.")
)
```
